Refinements for Open Automata

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
abstract

Establishing equivalence and refinement relations between programs is an important mean for 
verifying their correctness. By establishing that the
behaviours of a modified program simulate those of the source one, bisimulation relations formalise the desired relation between a specification and an implementation, 
 two equivalent implementations, or a program and its optimised implementation.
This article discusses a notion of refinement between \emph{open automata}, which are symbolic
behavioural models for communicating systems. 
Open automata may have \emph{holes} modelling elements of their
context, and can be composed by instantiation of the holes. This allows for a compositional approach for
verification of their behaviour.

We define refinement relations between systems including either equal or different sets of holes, and 
show under which conditions these refinements are preserved by composition of open automata.

>>>>

Establishing equivalence and refinement relations between programs is an important mean for 
verifying their correctness. By establishing that the
behaviours of a modified program simulate those of the source one, simulation relations formalise the desired relation between a specification and an implementation, 
 two equivalent implementations, or a program and its optimised implementation.
This article discusses a notion of simulation between \emph{open automata}, which are symbolic
behavioural models for communicating systems. 
Open automata may have \emph{holes} modelling elements of their
context, and can be composed by instantiation of the holes. This allows for a compositional approach for
verification of their behaviour.

We define a simulation between open automata that may or may not have the same holes, and 
show under which conditions these refinements are preserved by composition of open automata.
